Progress Report

### 2020-09-08 documentation/Optimization Work/08_27_20.tex
Working on optimization for arbitrary beamformer

In the following, we will assume that a matched filter is used at the transmitter. Further we will evaluate the performance of the system using the Mean Square Error given by 

@@

E\left[\|  \vs - (\mG + \Sigma_{i=1}^{N_S} \phi_i \mathbf{h}_{2,i}\mathbf{h}^T_{1,i})(\mG + \Sigma_{i=1}^{N_S} \phi_i \mathbf{h}_{2,i}\mathbf{h}^T_{1,i})^H\vs) \|^2 \right]

@@

in which we do not consider the noise at the receiver. 
In the following we assume that the elements of the IRS can not only adjust the phases of the impinging waves but may also be "turned off" such that they are not included in the channel.

@@

We leave all IRS elements \emph{on} to first find the full matched filter at the Tx. Assuming that we estimate the entire channel $\mH_{Total}$, we will not have sufficient information to estimate the individual components of the IRS component of the channel $\mathbf{h}_{2,i}\mathbf{h}^T_{1,i}$ and thus we cannot optimize with respect to $\phi_i $.

@@

E\left[\|  \vs - (\mG +  \mH_1 + \Sigma_{i=1}^{1} \phi_i \mathbf{h}_{2,i}\mathbf{h}^T_{1,i})(\mG +  \mH_1 + \Sigma_{i=1}^{1} \phi_i \mathbf{h}_{2,i}\mathbf{h}^T_{1,i})\vs  \|^2 \right]

@@

@@

		Note that once correlation is considered, we may want to decide the phase of elements in close proximity whose channels we have not yet estimated.

@@

Assuming $\mathbf{H}$ and $\mathbf{W}$ (The Tx linear precoder) to be constant over a coherence period, the expectation applies only to $\vs \vs^H$ 
and we consider equal power allocation at the transmitter such that the utility function becomes

@@

After finding the first $K \leq N_S$ IRS channels $\mathbf{h}_{2,i}\mathbf{h}^T_{1,i}$, the optimization problem with respect to the IRS phases for the case of a Matched Filter at the Tx is given by

@@

	    & \; \trace\left((\mI - \mathbf{H}\mathbf{H}^H)
	   (\mI - \mathbf{H}\mathbf{H}^H)^H \right)

@@

	    & \; - 2 \trace \left( \mathbf{H}\mathbf{H}^H\right) + \trace\left(\mathbf{H}\mathbf{H}^H \mathbf{H}\mathbf{H}^H\right)

@@

@@

	Expanding the above utility function and neglecting the terms without any phase coefficients, the above utility function becomes

@@

	the resulting components of the sum have entirely negative and real. In this case, each step of the algorithm solves the problem

@@

	in which $a \in \reals$ and $c \in \complex$ so the result is simply to choose $\phi_k$ to make $\phi_k c$ negative and real.
	The primary difficulty to performing such and optimization is finding the all values of $ c_i $ for each $\phi_{k}$ as each phase will be associated with 
	more than one $ c_i $ (particularly in the case of the matched filter precoder).
\section{Optimization Implementation}
To begin solving this problem I considered randomly selecting many complex numbers and corresponding phases in order to model the utility function 
	The algorithm then iterates through each $\phi_{k}$ shifts the phase such that the result is a negative real (only if this update improves the utility function).
\bibliography{bibliography}
\end{document}

>>>>

In the following, we will assume that a matched filter is used at the transmitter and we will evaluate the performance of the system using the Mean Square Error given by 

@@

E\left[\|  \vs - (\mG + \Sigma_{i=1}^{N_S} \phi_i \mathbf{h}_{2,i}\mathbf{h}^T_{1,i})\mathbf{W}\vs) \|^2 \right]

@@

in which $\mathbf{W}$ is the linear precoder at the transmitter. We do not consider the noise at the receiver in this utility function. 
In the following we assume that the elements of the IRS can adjust the phases of the impinging waves and may also be "turned off" such that they are not included in the channel.

@@

We leave all IRS elements \emph{on} to first find the full channel   $\mH_{Total}$(and then transmit this to the Tx). At this point, we will not have sufficient information to estimate the individual components of the IRS component of the channel $\mathbf{h}_{2,i}\mathbf{h}^T_{1,i}$ and thus we cannot optimize with respect to $\phi_i $.

@@

E\left[\|  \vs - (\mG +  \mH_1 + \Sigma_{i=1}^{1} \phi_i \mathbf{h}_{2,i}\mathbf{h}^T_{1,i})\mathbf{W}\vs  \|^2 \right]

@@

in which $\mH_{Total} =  \mH_1 + \Sigma_{i=1}^{1} \phi_i \mathbf{h}_{2,i}\mathbf{h}^T_{1,i}$

@@

		Note that once correlation is considered, the order in which the channels through each element $\mathbf{h}_{2,i}\mathbf{h}^T_{1,i}$ may impact the optimization performance .

@@

Assuming $\mathbf{H}$ and $\mathbf{W}$ to be constant over a coherence period, the expectation applies only to $\vs \vs^H$. If we consider equal power allocation at the transmitter, the utility function becomes

@@

After finding $K \leq N_S$ IRS element channels $\mathbf{h}_{2,i}\mathbf{h}^T_{1,i}$, the optimization problem with respect to the IRS phases for the case of a Matched Filter at the Tx is given by

@@

	    & \; \trace\left((\mI - \mathbf{H}\mathbf{W})
	   (\mI - \mathbf{H}\mathbf{W})^H \right)

@@

	    & \; - \trace \left( \mathbf{H}\mathbf{W}\right) - \trace \left( \mathbf{H}\mathbf{W}\right)^* +
	    \trace\left(\mathbf{H}\mathbf{W} \mathbf{W}^H \mathbf{H}^H\right)

@@

	\end{align}\label{mse_problem_full}

@@

	Expanding the above utility function and neglecting the terms without any phase coefficients, the cost function becomes

@@

	the corresponding component of the sum is real and negative. In this case, each step of the algorithm solves the problem

@@

	in which $a \in \reals$ and $c \in \complex$ so the result is simply to choose $\phi_k$ such that $\phi_k c$ is negative and real.

\section{Optimization Implementation}
To begin solving this problem I considered randomly selecting many complex numbers and corresponding phases in order to model the cost function 
	\begin{equation}
	\Sigma_{i=1}^{N} \left(\prod_{k=1}^{M_i}\phi_{k} c_i \right ) +  \Sigma_{i=1}^{N} \left(\prod_{k=1}^{M_i}\phi_{k} c_i \right)^H.
	\end{equation}
	The algorithm then iterates through each $\phi_{k}$ and shifts the phase such $\phi_{k} c_i$ a real and negative.
	Below is an example in which 100 numbers and their complex conjugates from $\mathcal{NC}(0,1)$ are assigned phase coefficients which are then used in the above optimization 
	problem. I have the algorithm for this test working but it is more difficult to apply this to the IRS case (numerical results) as I need to find the coefficient $c_i$ for each phase term.
	\par
	Next I considered the case in which an arbitrary linear precoding filter is used at the transmitter and the MSE is minimized.
	In this case, each step of the algorithm is the same as Problem \eqref{mse_problem_s}.

	 with the matched filter is finding the all values of $ c_i $ for each $\phi_{k}$ as each phase will be associated with more than one $ c_i $.
\bibliography{bibliography}
\end{document}
